Spikes demo

### 2018-09-27 analysis/spikesdemo.Rmd
wflow_publish("spikesdemo.Rmd")
A few minor revisions to the spikes demo.

Observe that the scale = 7 WCs are much more concentrated near zero
because the signal is smoother at this finer scale.

@@

Observe that the scale = 7 WCs are strongly shrunk toward zero,
whereas the scale = 1 WCs are not shrunk nearly as much; SMASH
infers from the data that the scale = 7 WCs are heavily concentrated
around zero, and consequently SMASH shrinks them more strongly.

Plot the observed wavelet coefficients (at scale 7 only) vs. the
"shrunken" wavelet coefficients estimated by adaptive shrinkage, and
how how the amount of shrinkage depends on the standard error (s.e.)
in the observations.

@@

From this plot, we see that SMASH shrinks WCs differently
depending on their precision; specifically, WCs that are less
precise---i.e., higher standard error (s.e.)---are shrunk more
strongly toward zero.

Finally, we plot the ground-truth signal (the mean function, drawn as
a black line) and the signals recovered by TI thresholding (light blue
line) and SMASH (the red line). The TI thresholding estimate shows
notable artifacts.

```{r plot-mean-signal-vs-estimates, fig.height=5, fig.width=10}
par(cex.axis = 1)
plot(mu.sp,type = "l",col = "black",lwd = 2,xlab = "position",ylab = "",
     ylim = c(-0.05,1),xaxp = c(0,1024,4),yaxp = c(0,1,4))
lines(mu.ti,col = "dodgerblue",lwd = 2)
lines(mu.smash,col = "orangered",lwd = 2)
```

>>>>

Observe that the scale = 7 WCs (dark blue) are much more concentrated
near zero because the signal is smoother at this finer scale.

@@

Observe that the scale = 7 WCs (dark blue) are strongly shrunk toward
zero, whereas the scale = 1 WCs (orange) are not shrunk nearly as
much; SMASH infers from the data that the scale = 7 WCs are heavily
concentrated around zero, and consequently SMASH shrinks them more
strongly.

Plot the observed wavelet coefficients (at scale 7 only) vs. the
"shrunken" wavelet coefficients estimated by adaptive shrinkage in
order to see how the amount of shrinkage depends on the standard error
(s.e.) in the observations.

@@

From this plot, it is evident that SMASH shrinks WCs differently
depending on their precision; specifically, WCs that are less
precise---i.e., higher standard error (s.e.)---are shrunk more
strongly toward zero.

Finally, we plot the ground-truth signal (the mean function, drawn as
a black line) and the signals recovered by TI thresholding (light blue
line) and SMASH (the red line).

```{r plot-mean-signal-vs-estimates, fig.height=5, fig.width=10}
par(cex.axis = 1)
plot(mu.sp,type = "l",col = "black",lwd = ,xlab = "position",ylab = "",
     ylim = c(-0.05,1),xaxp = c(0,1024,4),yaxp = c(0,1,4))
lines(mu.ti,col = "dodgerblue",lwd = 3)
lines(mu.smash,col = "orangered",lwd = 3)
```

In this example, the smoothed signal from SMASH is noticeably more
accurate than using TI thresholding (in which the variance is
estimated by running the median absolute deviation, or "RMAD",
method). The TI thresholding estimate shows notable artifacts.
